 ---
title: "Homework 4"
author: "Jenni Kane"
date: "March 16, 2021"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r}
data<-read.csv('Homework 4 Data.csv')
head(data)
```
```{r}
fit<-glm(formula= y ~ x1*x2, family=poisson, data = data)
summary(fit)
```
```{r}
b<-coef(fit)
b
```

Interpret the effect of variable x1 on the expected count when x2 is fixed at level "b". Verify your
interpretation in R.
```{r}
x1<-b[2]+b[4]
```
```{r}
x1
```
```{r}
exp(x1)
```

When x2 is fixed at level b, we would see a change of 1.460856 in the expected count (y) when x1 changes by one unit.

Verification:
```{r}
#evaluate value of log(y) when x1=1

x1_1<-b[1]+(b[2]*1)+(b[3]*1)+(b[4]*1*1)
x1_1
```

```{r}
#evaluate value of log(y) when x1=2

x1_2<-b[1]+(b[2]*2)+(b[3]*1)+(b[4]*1*2)
x1_2
```
```{r}
#recreate slope coefficient and compare to model output
log(exp(x1_2)/exp(x1_1));x1
```


Interpret the effect of variable x2 on the expected count when x1 is fixed at 1. Verify in R. 
```{r}
x2<-b[3]+b[4]
x2
```
```{r}
exp(x2)
```
When x1 is fixed at 1, we would see a change of .5665282 in the expected count (y) when variable x2 changes by one unit.

```{r}
x2_0<-b[1]+b[2]+(b[3]*0)+(b[4]*1*0)
x2_0
```

```{r}
x2_1<-b[1]+b[2]+(b[3]*1)+(b[4]*1*1)
x2_1
```

```{r}
log(exp(x2_1)/exp(x2_0)); x2
```

Predict the expected count, ± 95% confidence intervals, over the observed range of values of x1, assuming
x2 is fixed at level "b".
```{r}
new<- data.frame(
x1 = seq(min(data$x1), max(data$x1), length.out = 100),
x2 = factor(x = rep('b', times = 100),
levels = c('a', 'b')))

prd <- predict.glm(object = fit, newdata = new, type = 'link', se.fit = T)

low <- exp(prd$fit - qnorm(0.975) * prd$se.fit)
summary(low)
high <- exp(prd$fit + qnorm(0.975) * prd$se.fit)
summary(high)


plot(y = exp(prd$fit), x = new$x1, xlab = 'x1',
ylab = 'Expected count', cex.axis = 1.5, cex.lab = 1.5,
ylim = c(min(low), max(high)), type = 'l')+
lines(x = new$x1, y = low, lty = 2)+
lines(x = new$x1, y = high, lty = 2)
```
Predict the expected count, ± 95% confidence intervals, of levels "a" and "b", assuming x1 is fixed at
it's mean.

```{r}


new<-data.frame(x1=rep(mean(data$x1), times = 100),
                 x2= factor(x = data$x2))

prd <- predict.glm(object = fit, newdata = new, type = 'link', se.fit = T)
low <- exp(prd$fit - qnorm(0.975) * prd$se.fit)
summary(low)
high <- exp(prd$fit + qnorm(0.975) * prd$se.fit)
summary(high)

x2numeric<-as.data.frame(cbind(data$x2, ifelse(data$x2 == 'a', 0, 1)))
x2numeric[1]<-NULL

plot(y = exp(prd$fit), x = x2numeric$V2, xlab = 'x2',
ylab = 'Expected count', cex.axis = 1.5, cex.lab = 1.5,
ylim = c(min(low), max(high)), type = 'l')+
lines(x = x2numeric$V2, y = low, lty = 2)+
lines(x = x2numeric$V2, y = high, lty = 2)
```

