---
title: "Homework 1"
author: "Jenni Kane"
date: "2/10/2021"
output: html_document
---


Question 1 
Added a dummy variable for beach ID. Beach A=0, Beach B=1, Beach C=2.

```{r}
setwd("~/Desktop")
beach<-read.csv(file='beach.csv')
head(beach)
```
Question 2
```{r}
beach.model<-lm(formula=OpenBeach~Year*Dummy.ID, data = beach)
summary(beach.model)
```
```{r}
coefficients(beach.model)
```


```{r}
betas<-coefficients(beach.model)
```


Question 3
Beach A (dummy variable 0) in 1992
```{r}
betas[1]+(betas[2]+betas[4]*0)*1992+betas[3]*0
```

Beach B (dummy variable 1) in 1992
```{r}
betas[1]+(betas[2]+betas[4]*1)*1992+betas[3]*1
```

Beach C (dummy variable 2) in 1992

```{r}
betas[1]+(betas[2]+betas[4]*2)*1992+betas[3]*2
```


Question 4
```{r}
plot(beach$Year, beach$OpenBeach, xlab = 'Year', ylab = 'Open Beach Area')

```

Question 5

Rate of change at Beach A (dummy variable 0)

```{r}
betas[2]+(betas[4]*0)
```

Rate of change at Beach B (dummy variable 1)
```{r}
betas[2]+(betas[4]*1)
```

Rate of change at Beach C (dummy variable 2)
```{r}
betas[2]+(betas[4]*2)
```
Interpretation: 
Beach area is decreasing with time most rapidly at beach A, at a rate of 15.0912 area units per year. Beach C area is decreasing but at a much less rapid pace, at 0.7 area units per year. 
