---
title: "Exam 2"
author: "Jenni Kane"
date: "3/22/2021"
output: html_document
---
Question 1.
```{r}
data<-read.csv("Exam 2 Data.csv")
head(data)
```
Question 2
```{r}
fit<-glm(formula = y ~ x1*x2+x3, family = poisson, data = data)
summary(fit)
```
```{r}
b<-coef(fit)
b
```

Question 3: Interpret the effect of variable x1 when x2 = -1
```{r}
#effective slope of x1, when x2=-1
ex1<-b[2]+b[6]*-1
ex1
```
The log proportional change in expected count decreases by 0.75 for every 1-unit increase in x1.


Question 4. Plot expected counts ±90% confidence intervals over the observed range of variable x1. Assume variable when x2 = -1 and category "a".
```{r}
new<-data.frame(
  x1=seq(min(data$x1), max(data$x1), length.out = 100),
  x2 = -1, 
  x3 = factor('a', levels = c('a', 'b', 'c'))
)
predict<-predict.glm(fit, new, 'link', se.fit=T)
lo<-exp(predict$fit - qnorm(0.95) * predict$se.fit)
hi<-exp(predict$fit + qnorm(0.95) * predict$se.fit)

plot(y = exp(predict$fit), x = new$x1, xlab = 'x1', 
     ylab = 'Expected Count', cex.axis = 1.5, cex.lab = 1.5, 
     ylim=c(min(lo), max(hi)), type = 'l')
lines(x=new$x1, y = lo, lty = 2)
lines(x=new$x1, y = hi, lty = 2)
```
Question 5. Interpret the effect of variable x3
```{r}
exp(b[4])
```
The difference in expected count between categories b and a is 1.46.
```{r}
exp(b[5])
```
The difference in expected count between categories c and a is 0.41.

Question 6.
```{r}
library(multcomp)
```
```{r}
mx1<-mean(data$x1)
```
```{r}
mx2<-mean(data$x2)

mx1*mx2
```

```{r}
b
```
```{r}
m<-matrix(c(0,-.1320536, 0.03782269, -1, 1, -0.00499462), nrow = 1)
cnt<-glht(fit, m)
summary(cnt, test = adjusted('none'))
```
We can reject this null hypothesis and say that the difference in log expected count between levels b and c is not zero. 

Question 7. Derive the test statistic and p-value associated with the interaction between x1 and x2. What is the null hypothesis? Do we reject or fail to reject this null hypothesis? Defend your answer.
```{r}
s<-summary(fit)[['coefficients']][,2]
s
```
```{r}
ts<-b[6]/s[6]
ts
```
```{r}
pnorm(-1*abs(ts))*2
```
Interpretation: Our null hypothesis was that the slope coefficient for the interaction between x1 and x2 is 0. Since our p value is very small, we have strong evidence that the value of x1 depends on that of x2. 


Question 8:
```{r}
dbinom(c(1,0), size = 1, prob=(plogis(-2)))
```

Question 9: 
Bernoulli random variables take on values between 0 and 1, representing the probability of "success" in trials. Acceptable values are bounded between 0 and 1. Our link function, in this case the logit link, allows us to map a bounded quantity and map it to the real number line. Since we usually want to do the opposite, that is, map a number from the real number line to a probability between 0 and 1, we use the inverse logit link.

Question 10: We must assume asymptotic normality, or that they are Gaussian, with a mean of 0 and a standard deviation of 1. 


