---

title: "Homework 3"
author: "Jenni Kane"
date: "March 1, 2021"
output:
  html_document: default
  word_document: default
---
```{r}
setwd("C:/Users/jlp0043/Desktop")
data<-read.csv("Homework 3 Data.csv")
head(data)
```

Question 1
```{r}
fit<-glm(formula = y~x1+x2, family = binomial, data = data)
summary(fit)
```


```{r}
betas<-coef(fit)
betas
```

Question 2

```{r}
plogis(betas[2])
```
This is the log odds of a success as a function of the predictor variable, x2. So 0.46 is the change in log odds of success (getting y=1) associated with a one unit change in x2.

Question 3
```{r}
plogis(betas[3])
```
This is the log odds of a data point belonging to category b of our categorical variable.

Question 4 

Wald test for the effect of x1

```{r}
ts<-betas[2]/summary(fit)[['coefficients']]['x1', 'Std. Error']
ts
```


```{r}
p<-2*pnorm(-1*abs(ts), mean=0, sd=1)
p
```

Wald test for effect of x2
```{r}
ts<-betas[3]/summary(fit)[['coefficients']]['x2b', 'Std. Error']
ts
```

```{r}
p<-2*pnorm(-1*abs(ts), mean=0, sd=1)
p
```

Interpretation:

For x1, we fail to reject the null hypothesis since our p value suggests ~60% chance of observing a value more extreme than the test statisic by chance alone. However for variable x2 we can reject the null hypothesis since the probablility of observing a more extreme test statistic by chance is very low, around 2%, suggesting that we can be reasonably sure that this effect arises as a function of variable x2.

Question 5 

```{r}
x1<-seq(from=min(data$x1), to=max(data$x1), length.out = 100)
head(x1)
```
```{r}
y<-betas[1]+betas[2]*x1+betas[3]
y
plot(x=x1, y=plogis(y), ylab = "Probability of Success", xlab = "Value of x1")
```

