
---
title: "Homework 5"
author: "Jenni Kane"
date: "4/1/2021"
output: html_document
---

```{r}
data<-read.csv(file = "Bobcat.csv")
site<-read.csv(file = "psi covariates.csv")
detect<-read.csv(file = "p covariates.csv")
data_mat<-as.matrix(data)

```

```{r}
det_covs<-list(people = data.frame(detect[,]))
```

Questions 1 and 2
```{r}
library(unmarked)
occu_data<-unmarkedFrameOccu(y = data_mat, 
                             obsCovs = det_covs, 
                             siteCovs = site)

fit<-occu(formula = ~people ~Dist_5km, data = occu_data)

```

Call:
occu(formula = ~people ~ Dist_5km, data = occu_data)

Occupancy (logit-scale):
            Estimate    SE      z  P(>|z|)
(Intercept)    -1.05 0.101 -10.39 2.63e-25
Dist_5km      -23.64 4.773  -4.95 7.28e-07

Detection (logit-scale):
            Estimate     SE       z P(>|z|)
(Intercept)  -3.0133 0.0741 -40.646   0.000
people       -0.0609 0.3779  -0.161   0.872



Question 3
```{r}
plogis(-0.0609)
```

Probability of bobcat occurance when 10 people are photographed 
```{r}
p_10<- plogis(-3.0133+(-0.0609*10))
p_10
```

Probability of bobcat occurance when 11 people are photographed 
```{r}
p_11<-plogis(-3.0133+(-0.0609*11))
p_11
```
```{r}
recreated_slope<-log((p_11/(1-p_11))/ (p_10/(1-p_10)))
recreated_slope
```
```{r}
plogis(recreated_slope)
```

Hence, the log odds ratio associated with a 1 unit change in the number of people photographed is 0.48.

Question 4
```{r}
w<--23.64/4.773
w
```
```{r}
2*pnorm(-1*abs(w))
```
The null hypothesis was that there is no change in the probability of bobcat occupancy in response to land disturbance within 5km. Since our p value is so small, we can reliable reject this null hypothesis.

Question 5
```{r}
new_psi <- data.frame(Dist_5km = seq(from = min(site$Dist_5km),
            to = max(site$Dist_5km), length.out = 100))

predict<-predict(object=fit, newdata = new_psi, type = 'state')

plot(y=predict$Predicted, x=new_psi$Dist_5km, ylab = 'Probability of Bobcat Occurance', xlab='Proportion of area within 5km recently disturbed')
```

